---
title: "Dot Probe Task"
author: "Graham Albert"
date: "October 8 2020"
output: html_document
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load glmm.
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
####T
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
require(lsmeans)
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
library(readr)
DotProbe <- read_csv("DotProbe.csv")
View(DotProbe)
DotProbe=DotProbe[-c(1)]
```

####Lets obtain some summary statistics.
```{r}
summary(DotProbe)
dim(DotProbe)
View(DotProbe)
```

####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.
###We will exclude all incorrect responses from the data set.
```{r}
DotProbe_REDUCED<-DotProbe%>%
select(ID,Snellen_Denominator,Grip_Strength,Chest_Strength,Handness,Height, Weight,DomIPIP,TDScore,State,Trait,cue_image_1,cue_image_2,Face_Set_Code,Face_Type_Code_1,Face_Type_Code_2, Dominance_Score,cue_position_x_1,cue_position_x_2,target_position_x,conguruence,experimental_trials.thisN,experimental_trials.thisIndex,responsebutton.keys,responsebutton.corr, responsebutton.rt) %>%
filter(!responsebutton.corr %in% c('0'))
DotProbe_REDUCED
dim(DotProbe_REDUCED)
```

####The dependent variable is continuous and it is reaction time.
```{r}
require(dplyr)
DotProbe_REDUCED = mutate(DotProbe_REDUCED,ID = as.factor(DotProbe_REDUCED$ID), cue_image_1 = as.factor(DotProbe_REDUCED$cue_image_1),cue_image_2 = as.factor(DotProbe_REDUCED$cue_image_2),Face_Set_Code = as.factor(DotProbe_REDUCED$Face_Set_Code), Face_Type_Code_1 = as.factor(DotProbe_REDUCED$Face_Type_Code_1),Face_Type_Code_2 = as.factor(DotProbe_REDUCED$Face_Type_Code_2 ), cue_position_x_1 = as.factor(DotProbe_REDUCED$cue_position_x_1),cue_position_x_2  = as.factor(DotProbe_REDUCED$cue_position_x_2), target_position_x  = as.factor(DotProbe_REDUCED$target_position_x), conguruence=as.factor(DotProbe_REDUCED$conguruence), experimental_trials.thisN=as.factor(DotProbe_REDUCED$experimental_trials.thisN), Dominance_Score=as.factor(DotProbe_REDUCED$Dominance_Score),responsebutton.corr=as.factor(DotProbe_REDUCED$responsebutton.corr))
```
####To transform variables into numeric variables.
```{r}
DotProbe_REDUCED$DomIPIP =as.numeric(DotProbe_REDUCED$DomIPIP)
DotProbe_REDUCED$TDScore=as.numeric(DotProbe_REDUCED$TDScore)
DotProbe_REDUCED$State=(DotProbe_REDUCED$State)
DotProbe_REDUCED$Trait=(DotProbe_REDUCED$Trait)
```
####Now lets mutate level 2 predictors to standardizedthem
```{r}
DotProbe_REDUCED$zGrip_Strength=(DotProbe_REDUCED$Grip_Strength-mean(DotProbe_REDUCED$Grip_Strength))/(sd(DotProbe_REDUCED$Grip_Strength))
DotProbe_REDUCED$zChest_Strength=(DotProbe_REDUCED$Chest_Strength-mean(DotProbe_REDUCED$Chest_Strength))/(sd(DotProbe_REDUCED$Chest_Strength))
DotProbe_REDUCED$zHeight =(DotProbe_REDUCED$Height-mean(DotProbe_REDUCED$Height))/(sd(DotProbe_REDUCED$Height))
DotProbe_REDUCED$zWeight=(DotProbe_REDUCED$Weight-mean(DotProbe_REDUCED$Weight))/(sd(DotProbe_REDUCED$Weight))
DotProbe_REDUCED$zDomIPIP =(DotProbe_REDUCED$DomIPIP-mean(DotProbe_REDUCED$DomIPIP,na.rm=TRUE))/(sd(DotProbe_REDUCED$DomIPIP,na.rm=TRUE))
DotProbe_REDUCED$zTdom=(DotProbe_REDUCED$TDScore-mean(DotProbe_REDUCED$TDScore,na.rm=TRUE))/(sd(DotProbe_REDUCED$TDScore,na.rm=TRUE))
DotProbe_REDUCED$zState=(DotProbe_REDUCED$State-mean(DotProbe_REDUCED$State,na.rm=TRUE))/(sd(DotProbe_REDUCED$State,na.rm=TRUE))
DotProbe_REDUCED$zTrait=(DotProbe_REDUCED$Trait-mean(DotProbe_REDUCED$Trait,na.rm=TRUE))/(sd(DotProbe_REDUCED$Trait,na.rm=TRUE))
View(DotProbe_REDUCED)
```
####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(DotProbe_REDUCED$ID)
nlevels(DotProbe_REDUCED$cue_image_1)
nlevels(DotProbe_REDUCED$cue_image_2)
nlevels(DotProbe_REDUCED$Face_Set_Code)
nlevels(DotProbe_REDUCED$Face_Type_Code_1)
nlevels(DotProbe_REDUCED$Face_Type_Code_2)
nlevels(DotProbe_REDUCED$cue_position_x_1)
nlevels(DotProbe_REDUCED$cue_position_x_2)
nlevels(DotProbe_REDUCED$target_position_x)
nlevels(DotProbe_REDUCED$conguruence)
nlevels(DotProbe_REDUCED$Dominance_Score)
```
####Now let's windsorize our continuous dependent variable RT.



####Based on the inspection of the RT data it is not normally distributed. I will first look at a histogram to look at the distribution of the data.
```{r}
DotProbe_REDUCED=mutate(DotProbe_REDUCED,responsebutton.rt=as.numeric(DotProbe_REDUCED$responsebutton.rt))
hist(DotProbe_REDUCED$responsebutton.rt)
summary(DotProbe_REDUCED$responsebutton.rt)
```








###To make 
```{r}
DotProbe_MASTER=DotProbe_REDUCED
```



####Based on the inspection of the RT data it is not normally distributed. I will first look at a histogram to look at the distribution of the data.
```{r}

DotProbe_MASTER=mutate(DotProbe_MASTER,responsebutton.rt=as.numeric(DotProbe_MASTER$responsebutton.rt))
hist(DotProbe_MASTER$responsebutton.rt)
summary(DotProbe_MASTER$responsebutton.rt)
```
###To compute RT by subject.
```{r}
require(dplyr)
by_ID <- group_by(DotProbe_MASTER, ID)
head(by_ID)
by_ID_2<-summarize(by_ID,mean_RT = mean(responsebutton.rt, na.rm=TRUE), sd_RT = sd(responsebutton.rt, na.rm=TRUE), out_hi_RT = (mean_RT+2*(sd_RT)),out_low_RT = (mean_RT-2*(sd_RT)))
View(by_ID_2)
by_ID_3<-merge(by_ID,by_ID_2, by = c('ID'))
View(by_ID_3)
```

####Now I am going to filter out trials if they fall outside of +-3 SD from the participants mean
```{r}
require(dplyr)
by_ID_4=by_ID_3
by_ID_4$responsebutton.rt<-replace(by_ID_4$responsebutton.rt,by_ID_4$responsebutton.rt>by_ID_4$out_hi_RT, NA)
by_ID_4$responsebutton.rt<-replace(by_ID_4$responsebutton.rt,by_ID_4$responsebutton.rt<by_ID_4$out_low_RT, NA)
View(by_ID_4)
summary(by_ID_4)
```

####To view the windsorized rt.
```{r}
hist(by_ID_4$responsebutton.rt)
```


####To recode recall and encoding so that the reference category changes.
```{R}
DotProbe_MASTER$Face_Set_Code = factor(DotProbe_MASTER$Face_Set_Code,
                             levels = c(1,2),
                             labels = c("LSF", "NUSF"))
table(DotProbe_MASTER$Face_Set_Code)
DotProbe_MASTER$Face_Type_Code_1= factor(DotProbe_MASTER$Face_Type_Code_1 ,
                             levels = c(1,2,3),
                             labels = c("FEM", "MASC","Reg"))
table(DotProbe_MASTER$Face_Type_Code_1)
DotProbe_MASTER$Face_Type_Code_2= factor(DotProbe_MASTER$Face_Type_Code_2 ,
                             levels = c(1,2,3),
                             labels = c("FEM", "MASC","Reg"))
table(DotProbe_MASTER$Face_Type_Code_2)
DotProbe_MASTER$cue_position_x_1= factor(DotProbe_MASTER$cue_position_x_1 ,
                             levels = c(-2,2),
                             labels = c("LEFT", "RIGHT"))
table(DotProbe_MASTER$cue_position_x_1)
DotProbe_MASTER$cue_position_x_2= factor(DotProbe_MASTER$cue_position_x_2 ,
                             levels = c(-2,2),
                             labels = c("LEFT", "RIGHT"))
table(DotProbe_MASTER$cue_position_x_2)
DotProbe_MASTER$target_position_x = factor(DotProbe_MASTER$target_position_x,
                             levels = c(-2,2),
                             labels = c("LEFT", "RIGHT"))
table(DotProbe_MASTER$target_position_x)
DotProbe_MASTER$conguruence  = factor(DotProbe_MASTER$conguruence,
                             levels = c(0,1),
                             labels = c("INCON", "CON"))
table(DotProbe_MASTER$conguruence)
DotProbe_MASTER$Dominance_Score  = factor(DotProbe_MASTER$Dominance_Score,
                             levels = c(3,2,6),
                             labels = c("RegVFem", "MascVFem","MascVRegular"))
table(DotProbe_MASTER$Dominance_Score)
```





####Now lets conduct the multi-level model.
####The dependent variables is reaction time.
####The level 1 fixed effects are dominance score (i.e., whether the face is masculinized or feminized), 
####conguruence (referred to is trial type in the manuscript: refers to whether the target shape was presented in the same visual field as the target face or the opposite visual field.
####target_position_x which is referred to as target location (i.e., presented in the left or right visual field)
####The level 2 fixed effects are trait dominance and trait anxiety.
####The random effects are cue image (i.e., the image presented for that trial) and participant.



####Lets add level 2 fixed effects.


####Dominance and anxiety
```{r}
require(lme4)
M1 = glmer(data=DotProbe_MASTER,responsebutton.rt~Dominance_Score*conguruence*target_position_x*zDomIPIP+zTrait+(1|ID:cue_image_1), family=Gamma(link ="inverse"), glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e9)))
summary(M1)
```

####To inspect the interaction with lsmeans.
```{r}
require(lsmeans)
lsmeans(M1, list(pairwise ~Dominance_Score:conguruence:target_position_x:zDomIPIP))
```
####To explore the interaction
```{r}
require(lsmeans)
lsmeans(M1, list(pairwise ~conguruence:target_position_x), adjust = "holm")
```

####To explore the interaction
```{r}
require(lsmeans)
lsmeans(M1, list(pairwise ~Dominance_Score:target_position_x), adjust = "holm")
```


####To explore the interaction
```{r}
require(lsmeans)
lsmeans(M1, list(pairwise ~Dominance_Score), adjust = "holm")
```

####Lets compute the means for RT by morph type.
```{r}
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$Dominance_Score,DotProbe_MASTER$conguruence), na.rm=TRUE, mean)
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$Dominance_Score,DotProbe_MASTER$conguruence),  na.rm=TRUE,sd)
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$Dominance_Score,DotProbe_MASTER$conguruence), length)
```




####Lets compute the means for RT by morph type.
```{r}
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$conguruence), na.rm=TRUE, mean)
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$conguruence),  na.rm=TRUE,sd)
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$conguruence), length)
```

####Lets compute the means for RT by morph type.
```{r}
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$target_position_x), na.rm=TRUE, mean)
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$target_position_x),  na.rm=TRUE,sd)
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$target_position_x), length)
```

####Lets compute the means for RT by morph type.
```{r}
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$Dominance_Score,DotProbe_MASTER$target_position_x), na.rm=TRUE, mean)
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$Dominance_Score,DotProbe_MASTER$target_position_x),  na.rm=TRUE,sd)
tapply(DotProbe_MASTER$responsebutton.rt, list(DotProbe_MASTER$Dominance_Score,DotProbe_MASTER$target_position_x), length)
```
####To obtain the ICC for models 2.
```{r}
require(sjstats)
performance::icc(M1)
```
##Now let's get the confidence intervals for our model.
```{r}
se<- sqrt(diag(vcov(M1)))
View(se)
#generate table of estimates with 95% CI
(tab<-cbind(Est = fixef(M1), LL=fixef(M1)-1.96*se, UL=fixef(M1)+1.96*se))
View(tab)
```
###To visual model.
```{r}
require(effects)
e <- allEffects(M1)
print(e)
plot(e)
```

# allEffects() returns a list, but for our model (where everything can interact with everything), there's only one element
```{r}
plot(e,multiline=TRUE,confint=TRUE,ci.style="bars"
     ,main="Effects of Face Morphs on RT"
     ,xlab="Face Type"
     ,ylab="Reaction Time")
```



####Let's generate the AIC for the 8 models.
```{r}
require(AICcmodavg)
print(aictab(list(M1), c("M1"), LL = FALSE))
```

####Let's use ggplot to create a regression plot for the data.
```{r}
require(sjPlot)
library(sjmisc)
plot_model(M1)
```

