---
title: "Flanker Task"
author: "Graham Albert"
date: "October 8 2020"
output: html_document
---


###To load required packarges
```{r}
require(curl) 
```
######loading data
#####for more advanced rotation.
```{r}
require(dplyr)
```
####for data manipulation.
```{r}
require(yaml)
require(stringi)
```
####for correlation plot depiction.
```{r}
require(gplots)
require(ggplot2)
require(gridExtra)
require(moments)
```

###To load glmm.
```{r}
require(lme4)
require(AICcmodavg)
require(MuMIn)
require(r2glmm)
```
####T
```{r}
require(RColorBrewer) # needed for some extra colours in one of the graphs
require(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
```


####To load my data set for the mating motivation scale into the  R work space.
```{r}
library(readr)
FlankerTask <-  read_csv("Flanker Task.csv")
View(FlankerTask)
FlankerTask=FlankerTask[-c(1)]
```

####Lets obtain some summary statistics.
```{r}
summary(FlankerTask)
dim(FlankerTask)
View(FlankerTask)
```
###We will exclude all incorrect answers.
```{r}

FlankerTask_REDUCED <-FlankerTask_REDUCED%>% 
select(ID, Snellen_Denominator,Grip_Strength,Chest_Strength,Handness,Height, Weight, DomIPIP,Tdom,State,Trait,cue_image_1,Face_Set_Code, Face_Type_Code,letter,corAns,orientation,experimental_trials.thisN,experimental_trials.thisIndex,responsebutton.keys,responsebutton.corr, responsebutton.rt) %>%
filter(!responsebutton.corr %in% c('0'))
FlankerTask_REDUCED
dim(FlankerTask_REDUCED)
```
####Lets factor the variables which we are going to use as our random and fixed effects and append them to the data set.

####The dependent variable is continuous and it is reaction time.
```{r}
require(dplyr)
FlankerTask = mutate(FlankerTask_REDUCED,ID = as.factor(FlankerTask_REDUCED$ID), cue_image_1 = as.factor(FlankerTask_REDUCED$cue_image_1), Face_Set_Code = as.factor(FlankerTask_REDUCED$Face_Set_Code), Face_Type_Code = as.factor(FlankerTask_REDUCED$Face_Type_Code), orientation =as.factor(FlankerTask_REDUCED$orientation), experimental_trials.thisN=as.factor(FlankerTask_REDUCED$experimental_trials.thisN),letter=as.factor(FlankerTask_REDUCED$letter),  responsebutton.corr=as.factor(FlankerTask_REDUCED$ responsebutton.corr))
```
####To transform variables into numeric variables.
```{r}
FlankerTask$DomIPIP =as.numeric(FlankerTask$DomIPIP)
FlankerTask$Tdom=as.numeric(FlankerTask$Tdom)
FlankerTask$State=(FlankerTask$State)
FlankerTask$Trait=(FlankerTask$Trait)
```
####Now lets mutate level 2 predictors to standardizedthem
```{r}
FlankerTask$zGrip_Strength=(FlankerTask$Grip_Strength-mean(FlankerTask$Grip_Strength))/(sd(FlankerTask$Grip_Strength))
FlankerTask$zChest_Strength=(FlankerTask$Chest_Strength-mean(FlankerTask$Chest_Strength))/(sd(FlankerTask$Chest_Strength))
FlankerTask$zHeight =(FlankerTask$Height-mean(FlankerTask$Height))/(sd(FlankerTask$Height))
FlankerTask$zWeight=(FlankerTask$Weight-mean(FlankerTask$Weight))/(sd(FlankerTask$Weight))
FlankerTask$zDomIPIP =(FlankerTask$DomIPIP-mean(FlankerTask$DomIPIP,na.rm=TRUE))/(sd(FlankerTask$DomIPIP,na.rm=TRUE))
FlankerTask$zTdom=(FlankerTask$Tdom-mean(FlankerTask$Tdom,na.rm=TRUE))/(sd(FlankerTask$Tdom,na.rm=TRUE))
FlankerTask$zState=(FlankerTask$State-mean(FlankerTask$State,na.rm=TRUE))/(sd(FlankerTask$State,na.rm=TRUE))
FlankerTask$zTrait=(FlankerTask$Trait-mean(FlankerTask$Trait,na.rm=TRUE))/(sd(FlankerTask$Trait,na.rm=TRUE))
View(FlankerTask)
```



####Lets determine if we effectively factors the variables of interested.
###We will determine the number of levels for each factor.
```{r}
nlevels(FlankerTask$ID)
nlevels(FlankerTask$cue_image_1)
nlevels(FlankerTask$Face_Set_Code)
nlevels(FlankerTask$Face_Type_Code)
nlevels(FlankerTask$letter)
nlevels(FlankerTask$orientation)
nlevels(FlankerTask$experimental_trials.thisN)
```

####Based on the inspection of the RT data it is not normally distributed. I will first look at a histogram to look at the distribution of the data.
```{r}
FlankerTask=mutate(FlankerTask,responsebutton.rt=as.numeric(FlankerTask$responsebutton.rt))
hist(FlankerTask$responsebutton.rt)
summary(FlankerTask$responsebutton.rt)
```








###To make 
```{r}
FlankerTask_MASTER=FlankerTask
```
####To recode recall and encoding so that the reference category changes.
```{R}
FlankerTask_MASTER$Face_Set_Code = factor(FlankerTask_MASTER$Face_Set_Code,
                             levels = c(1,2),
                             labels = c("LSF", "NUSF"))
table(FlankerTask_MASTER$Face_Set_Code)
FlankerTask_MASTER$Face_Type_Code= factor(FlankerTask_MASTER$Face_Type_Code,
                             levels = c(1,2,3),
                             labels = c("FEM", "MASC","Reg"))
table(FlankerTask_MASTER$Face_Type_Code)
FlankerTask_MASTER$orientation= factor(FlankerTask_MASTER$orientation ,
                             levels = c(0,180),
                             labels = c("Rightsideup","Upsidedown"))
table(FlankerTask_MASTER$orientation)
FlankerTask_MASTER$letter= factor(FlankerTask_MASTER$letter ,
                             levels = c(1,2),
                             labels = c("L", "T"))
table(FlankerTask_MASTER$letter)
```


####Based on the inspection of the RT data it is not normally distributed. I will first look at a histogram to look at the distribution of the data.
```{r}
FlankerTask_MASTER=mutate(FlankerTask_MASTER,responsebutton.rt=as.numeric(FlankerTask_MASTER$responsebutton.rt))
hist(FlankerTask_MASTER$responsebutton.rt)
summary(FlankerTask_MASTER$responsebutton.rt)
```
###To compute RT by subject.
```{r}
require(dplyr)
by_ID <- group_by(FlankerTask_MASTER, ID)
head(by_ID)
by_ID_2<-summarize(by_ID,mean_RT = mean(responsebutton.rt, na.rm=TRUE), sd_RT = sd(responsebutton.rt, na.rm=TRUE), out_hi_RT = (mean_RT+2*(sd_RT)),out_low_RT = (mean_RT-2*(sd_RT)))
View(by_ID_2)
by_ID_3<-merge(by_ID,by_ID_2, by = c('ID'))
View(by_ID_3)
summary(by_ID_3)
```

####Now I am going to filter out trials if they fall outside of +-3 SD from the participants mean
```{r}
require(dplyr)
by_ID_4=by_ID_3
by_ID_4$responsebutton.rt<-replace(by_ID_4$responsebutton.rt,by_ID_4$responsebutton.rt>by_ID_4$out_hi_RT, NA)
by_ID_4$responsebutton.rt<-replace(by_ID_4$responsebutton.rt,by_ID_4$responsebutton.rt<by_ID_4$out_low_RT, NA)
View(by_ID_4)
summary(by_ID_4)
```

####To view the windsorized rt.
```{r}
hist(by_ID_4$responsebutton.rt)
```


###To override FlankerTask master.
```{r}
FlankerTask_MASTER=by_ID_4
```

####Now lets conduct the multi-level model.
####The dependent variables is reaction time.
####The level 1 fixed effects are morph type (i.e., whether the face is masculinized or feminized), 

####The level 2 fixed effects are trait dominance and trait anxiety.
####The random effects are cue image (i.e., the image presented for that trial) and participant.

```{r}
require(lme4)
M1 = glmer(data=FlankerTask_MASTER,responsebutton.rt~Face_Type_Code*zDomIPIP*zTrait+(1|ID:cue_image_1), family=Gamma(link ="inverse"), glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(M1)
```





##Now let's get the confidence intervals for our model.
```{r}
se<- sqrt(diag(vcov(M1)))
View(se)
#generate table of estimates with 95% CI
(tab<-cbind(Est = fixef(M1), LL=fixef(M1)-1.96*se, UL=fixef(M1)+1.96*se))
View(tab)
```
####To obtain the ICC for models 2.
```{r}
require(sjstats)
performance::icc(M1)
```


####Let's use ggplot to create a regression plot for the data.
```{r}
require(sjPlot)
library(sjmisc)
plot_model(M1)
```
